---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# DSBswirl

This R package provides the swirl courses, including an installation function, developed for the DSB (Data Science in Biology) program within the Biology Department of the University of Hamburg (UHH).

The following swirl courses (in German) are currently included:

- DSB-01: Basics in R (R Grundlagen)
- DSB-02: Data exploration with R (Datenexploration mit R)
- DSB-03: Data wrangling and introduction to tidyverse (Datenaufbereitung oder per Anleitung durchs Tidyversum)
- DSB-04: Data visualization with ggplot2 (Datenvisualisierung mit ggplot2)
- DSB-05: Working with special data types (Handling spezieller Datentypen)
- DSB-06: Advanced R programming (Fortgeschrittene R Programmierung)

There is an additional English swirl course, *Data analysis with R*, covering R basics, data wrangling and visualization with the tidyverse, and linear regression modelling.


## Package installation

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("uham-bio/DSBswirl")
```


## Course installations

```{r, eval=FALSE}
# Install all courses (default)
DSBswirl::install_dsb_courses()

# Install only course DSB-01 (R basics)
DSBswirl::install_dsb_courses(courses = "DSB-01")

# Install the course DSB-01, DSB-04, and DSB-05
DSBswirl::install_dsb_courses(courses = c("DSB-01", "DSB-04", "DSB-05"))
```

---

<br><br><br>
Last Update: 24/09/2025

- Replaced the deprecated ggplot 2 functions `coord_trans()` and `borders()` with the new functions `coord_transform()` (since 4.0.0 release) and `annotation_borders()` (since 3.4.0).
